The challenge and promise of software citation for credit, identification, discovery, and reuse

### 2016-06-26 SC-challenge.tex
shortened 2nd research challenge solution
slight change of table dimensions to shorten
shortening table a bit more

Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University;
A.\ M.\ Smith,
GitHub, Inc.;
D.\ S.\ Katz,
National Center for Supercomputing Applications \& Graduate School of Library and Information Science, University of Illinois at Urbana--Champaign;
emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
\end{bottomstuff}

@@

\rowcolors{2}{}{lightgray}
\begin{table}[htbp]%
\tbl{Key research challenges and possible solutions\slash methods\label{tab:challenges}}{%
\begin{tabular}{@{}p{0.38\linewidth}p{0.58\linewidth}@{}}
\toprule
\textbf{Key research challenge} & \textbf{Possible solutions/methods} \\
\midrule

@@

Establish mechanisms for software to cite other software (i.e., dependencies) &
Software publication as software papers allows this. For software that is directly published, this is an open challenge with no obvious path forward \\

Develop infrastructure to support indexing of software citations along with (or complementary to) the existing publication citation ecosystem &
The FORCE11 Software Citation Implementation Working Group will also work on this, in collaboration with publishers and indexers \\

@@

>>>>

Author's addresses: K.\ E.\ Niemeyer, School of Mechanical, Industrial, and Manufacturing Engineering, Oregon State University;
A.\ M.\ Smith,
GitHub, Inc.;
D.\ S.\ Katz,
NCSA \& iSchool \& ECE, University of Illinois at Urbana--Champaign;
emails: \href{mailto:kyle.niemeyer@oregonstate.edu}{kyle.niemeyer@oregonstate.edu}, \href{mailto:arfon@github.com}{arfon@github.com}, \href{mailto:d.katz@ieee.org}{d.katz@ieee.org}
\end{bottomstuff}

@@

\rowcolors{2}{}{lightgray}
\begin{table}[htbp]%
\tbl{Key research challenges and possible solutions\slash methods\label{tab:challenges}}{%
\begin{tabular}{@{}p{0.37\linewidth}p{0.60\linewidth}@{}}
\toprule
\textbf{Key research challenge} & \textbf{Possible solutions/methods} \\
\midrule

@@

Establish mechanisms for software to cite other software (i.e., dependencies) &
Software publication as software papers allows this. For software that is directly published, this is an open challenge\\ % with no obvious path forward \\

Develop infrastructure to support indexing of software citations %along with (or complementary to)
within the existing publication citation ecosystem &
The FORCE11 Software Citation Implementation Working Group will also work on this, in collaboration with publishers and indexers \\

@@

\vspace{-2mm}
